|

### 2024-08-10 doc/paper.qmd
results section

# Introduction {#sec-introduction}

The aim of this paper is to illustrate the use of open science tools in empirical accounting research.

@@

# Research Design Choices and Assumptions {#sec-research_design_assumptions}

The aim of Assignment III is to replicate a specific empirical table (Table 2 Panel A) from the seminal paper by @Leuz_2003. This table involves calculating the EM measures for firms across various countries over a defined period and examining the relationship between these measures and investor protection. The replication process includes data loading, preparation, cleaning, and normalization, followed by the application of statistical methods to compute and interpret financial metrics. For Assignment III, I pulled data from the Worldscope database through WRDS and used the Python programming language to carry out the empirical analysis. Visual Studio Code was used as the Integrated Development Environment (IDE) for writing, debugging, and optimizing the Python code.

@@

# Results {#sec-results}
The comparison between the calculated EM1 values and those reported in the original paper reveals a strong alignment, with only minor differences observed across most countries. The overall pattern of EM1 values is consistent, effectively capturing the underlying trends in earnings management across different countries. Any differences, such as those for the Philippines, Taiwan, and Norway, are relatively small and likely due to variations in data sources, updates, or slight methodological differences as outlined in @sec-research_design_assumptions. The summary statistics (mean, median, min, max and standard deviation) also closely match those in the original study, further supporting the robustness of the replication process. The results indicate that Anglo-American countries tend to have higher EM1 values, suggesting less earnings smoothing compared to Continental Europe and Asia, consistent with the conclusion of @Leuz_2003 that earnings are smoother in Continental Europe and Asia than in Anglo-American countries, after controlling for the volatility of cash flows.

@@

The replicated EM3 results are very similar to those of the original study, with close alignment in summary statistics and consistent identification of South Africa and Germany as the countries with the minimum and maximum EM3 values. Additionally, the replication confirms that the magnitude of firms’ accruals relative to their operating cash flows is smaller in the U.K. and the U.S. compared to Austria, Germany, and South Korea, consistent with the original findings.

@@

The comparison between the original and replicated aggregate earnings management scores reveals a strong overall alignment with consistent key trends. In the original study, Austria and Greece are at the top of the rankings with aggregate scores of 28.3, indicating the highest levels of earnings management. In the replication, Greece and Austria remain at the top with slightly adjusted scores of 27.5 and 27.2, respectively. Taiwan and South Korea also rank high, mirroring their positions in the original study. While some differences in specific rankings and scores exist, such as the United States consistently having the lowest level of earnings management (2.0 in the original and 3.5 in the replication), these variations are minor and do not spoil overall consistency.

In summary, the replication effectively captures the original study’s key findings, confirming that European and Asian countries generally exhibit higher levels of earnings management than their Anglo-American counterparts. The strong similarity between the original and replicated results underscores the robustness and reliability of the findings.

# Conclusion {#sec-conclusion}

##gpt: Summarize the key findings and their significance.

@@

The analysis revealed that

The replication yields mixed results. While

@@

The replicated analysis also reveals that the individual earnings management measures are highly correlated, leading to similar rankings across the four measures and the aggregate earnings management score. This consistency supports the original study’s finding that a single underlying factor likely represents the four individual measures. In line with the original results, the replicated country rankings based on the aggregate score show high ranks for countries like Greece, Austria, and South Korea, and lower ranks for countries such as Australia, the U.K., and the U.S. This reinforces the robustness of the aggregated measure in capturing the overall level of earnings management across different countries.

>>>>

# Introduction {#sec-introduction}
The aim of this paper is to illustrate the use of open science tools in empirical accounting research.

@@

# Research Design Choices and Assumptions {#sec-research_design_assumptions}
The aim of Assignment III is to replicate a specific empirical table (Table 2 Panel A) from the seminal paper by @Leuz_2003. This table involves calculating the EM measures for firms across various countries over a defined period and examining the relationship between these measures and investor protection. The replication process includes data loading, preparation, cleaning, and normalization, followed by the application of statistical methods to compute and interpret financial metrics. For Assignment III, I pulled data from the Worldscope database through WRDS and used the Python programming language to carry out the empirical analysis. Visual Studio Code was used as the Integrated Development Environment (IDE) for writing, debugging, and optimizing the Python code.

@@

# Results {#sec-results}
The comparison between the calculated EM1 values and those reported in the original paper reveals a strong alignment, with only minor differences observed across most countries. The overall pattern of EM1 values is consistent, effectively capturing the underlying trends in earnings management across different countries. Any differences, such as those for the Philippines, Taiwan, and Norway, are relatively small and likely due to variations in data sources, updates, or slight methodological differences, as outlined in @sec-research_design_assumptions. The summary statistics (mean, median, min, max, and standard deviation) also closely match those in the original study, further supporting the robustness of the replication process. The results indicate that Anglo-American countries tend to have higher EM1 values, suggesting less earnings smoothing compared to Continental Europe and Asia, consistent with the conclusion of @Leuz_2003 that earnings are smoother in Continental Europe and Asia than in Anglo-American countries after controlling for the volatility of cash flows.

@@

The replicated EM3 results are very similar to those of the original study, with close alignment in summary statistics and consistent identification of South Africa and Germany as the countries with the minimum and maximum EM3 values. Additionally, the replication confirms that the magnitude of firms' accruals relative to their operating cash flows is smaller in the U.K. and the U.S. compared to Austria, Germany, and South Korea, consistent with the original findings.

@@

The comparison between the original and replicated aggregate earnings management scores reveals a strong overall alignment with consistent key trends. In the original study, Austria and Greece are at the top of the rankings with aggregate scores of 28.3, indicating the highest levels of earnings management. In the replication, Greece and Austria remain at the top with slightly adjusted scores of 27.5 and 27.2, respectively. Taiwan and South Korea also rank high, mirroring their positions in the original study. While some differences in specific rankings and scores exist, such as the United States consistently having the lowest level of earnings management (2.0 in the original and 3.5 in the replication), these variations are minor and do not undermine the overall consistency.

In summary, the replication effectively captures the original study's key findings, confirming that European and Asian countries generally exhibit higher levels of earnings management than their Anglo-American counterparts. The strong similarity between the original and replicated results underscores the robustness and reliability of the findings.

# Conclusion {#sec-conclusion}
##gpt: Summarize the key findings and their significance.

@@

@@

The replication analysis also reveals that the individual earnings management measures are highly correlated, leading to similar rankings across the four measures and the aggregate earnings management score. This consistency supports the original study’s finding that a single underlying factor likely represents the four individual measures. In line with the original results, the replicated country rankings based on the aggregate score show high ranks for countries like Greece, Austria, and South Korea, and lower ranks for countries such as Australia, the U.K., and the U.S. This reinforces the robustness of the aggregated measure in capturing the overall level of earnings management across different countries.
